---
title: "ReceivingNews first wave - power simulation"
editor_options: 
  markdown: 
    wrap: 72
---
 
```
By Valentin Guigon
June 2023
```


```{r, setup, include=FALSE}
rm(list = ls(all.names = TRUE)) #will clear all objects includes hidden objects.
gc() #free up memory and report the memory usage

list.of.packages=c("lme4", "magrittr", "dplyr", "stringr", "simr",
                   "rprojroot")
{
  new.packages <- list.of.packages[!(list.of.packages %in% installed.packages()[,"Package"])]
  if(length(new.packages)) install.packages(new.packages)
  lapply(list.of.packages, require, character.only = TRUE)
}

project_root = find_rstudio_root_file()

```



```{r ,load data and variables, include=FALSE}
load(paste("../../R_environments/ReceivingNews2-power_simulation_env.RData", sep=""))
```



# Power simulation at the first wave
We hypothesized that participants' veracity estimation was significantly explained by news' content uncertainty, as assessed by news' content precision level (i.e., *Imprecision*). After a first acquisition of data, with n=79, we simulate the current power for the fixed simple effect of the variable *Imprecision*, and for the fixed interaction effect of the variable *Imprecision* with the variable *Veracity*. Then we simulate the power for lower fixed effects and more participants. We set up the number of simulations at 100.

# I. Full control model
We formulated a model with control variables but removed complexity from the random structure to save computation time. 
The model is written with the form:
```
Success ~ Veracity*Imprecision + Veracity*Polarization + Confidence + Veracity*Theme + 
Age + Sex + Education + Ec + (1|Subject)
```

## A. Current power

We simulate the current power for our model. Effect sizes are:
- Imprecision: `r summary(mSuccessAmbig)$coefficients[3,1]` (odds-ratio = `r exp(summary(mSuccessAmbig)$coefficients[3,1])`)
- Polarization: `r summary(mSuccessAmbig)$coefficients[4,1]` (odds-ratio = `r exp(summary(mSuccessAmbig)$coefficients[4,1])`)
- Interaction of imprecision with veracity judgment: `r summary(mSuccessAmbig)$coefficients[14,1]` (odds-ratio = `r exp(summary(mSuccessAmbig)$coefficients[14,1])`)
- Interaction of polarization with veracity judgment: `r summary(mSuccessAmbig)$coefficients[15,1]` (odds-ratio = `r exp(summary(mSuccessAmbig)$coefficients[15,1])`)

The current power for the interaction of imprecision with veracity judgment is:

```{r ReceivingNews2 Model1 Imprecision interaction effect power sim, echo=FALSE}
ps2_mSuccessImprec
```

The current power for the interaction of polarization with veracity judgment is:

```{r ReceivingNews2 Model1 Polarization interaction effect power sim, echo=FALSE}
ps4_mSuccessPolar
```



## B. Simulation of power

We simulate the power for Imprecision and Polarization simple effects with 80, 150, 200 and 250 subjects. The simulated power is:

```{r ReceivingNews2 Model 1 Imprecision simple effect predicted power, echo=FALSE}
pc_mSuccess2_fixed_extended_Imprec
```

```{r ReceivingNews2 Model 1 Polarization simple effect predicted power, echo=FALSE}
pc_mSuccess2_fixed_extended_Polar
```

**However the computation time is too high (>3h)**





# II. Simpler model

To save computation time, we remove the sociodemographics variables. The model is now written with the form:
```
Success ~ Veracity * Imprecision + Veracity * Polarization + Confidence + Veracity * Theme + (1 | Subject)
```

We simulate the current power for our model. Effect sizes are:
- Imprecision: `r summary(mSuccessAmbig2)$coefficients[3,1]` (odds-ratio = `r exp(summary(mSuccessAmbig2)$coefficients[3,1])`)
- Polarization: `r summary(mSuccessAmbig2)$coefficients[4,1]` (odds-ratio = `r exp(summary(mSuccessAmbig2)$coefficients[4,1])`)
- Interaction of imprecision with veracity judgment: `r summary(mSuccessAmbig2)$coefficients[7,1]` (odds-ratio = `r exp(summary(mSuccessAmbig2)$coefficients[7,1])`)
- Interaction of polarization with veracity judgment: `r summary(mSuccessAmbig2)$coefficients[8,1]` (odds-ratio = `r exp(summary(mSuccessAmbig2)$coefficients[8,1])`)


## A. Actual effect size
We simulate the power for 80, 150, 200 and 250 subjects. The simulated power is:

```{r ReceivingNews2 Model 2 Imprecision simple effect predicted power - Plot, echo=FALSE}
plot(pc_mSuccess2_fixed_extended_Imprec)
```

```{r ReceivingNews2 Model 2 Polarization simple effect predicted power - Plot, echo=FALSE}
plot(pc_mSuccess2_fixed_extended_Polar)
```


## B. Low effect size
We lower *Imprecision* fixed main effect at -0.05 (initially at -0.2): 
The simulated power is:

```{r ReceivingNews2 Model 2 low Imprecision simple effect predicted power - Plot, echo=FALSE}
plot(pc_mSuccessAmbig3_fixed_extended_Imprec)
```

We lower *Polarization* fixed main effect at -0.05 (initially at -0.17): 
The simulated power is:

```{r ReceivingNews2 Model 2 low Polarization simple effect predicted power - Plot, echo=FALSE}
plot(pc_mSuccessAmbig3_fixed_extended_Polar)
```

The effect size is too low to have good power. 


## C. Mid effet size

### Simple effect with 250 subjects
We lower *Imprecision* fixed main effect at -0.1 (initially at -0.2):

```{r ReceivingNews2 Model 2 mid Imprecision simple effect predicted power - Plot, echo=FALSE}
plot(pc_mSuccessAmbig4_fixed_extended_Imprec)
```

We detect an effect size as low as -.1 with power >92% from 200 subjects.


We lower *Polarization* fixed main effect at -0.1 (initially at -0.2):

```{r ReceivingNews2 Model 2 mid Polarization simple effect predicted power - Plot, echo=FALSE}
plot(pc_mSuccessAmbig4_fixed_extended_Polar)
```

We detect an effect size as low as -.1 with power >92% from 250 subjects.


### Interaction effects with 250 subjects

We simulate the power for Imprecision interacting with Veracity with 80, 150, 200 and 250 subjects and lower the fixed effect at -0.25. The simulated power is:

```{r ReceivingNews2 Model 2 Imprecision interaction effect predicted power - Plot, echo=FALSE}
plot(pc_mSuccessAmbig5_fixed_extended_Imprec)
```


We simulate the power for Polarization interacting with Veracity with 80, 150, 200 and 250 subjects and lower the fixed effect at -0.25. The simulated power is:

```{r ReceivingNews2 Model 2 Polarization interaction effect predicted power - Plot, echo=FALSE}
plot(pc_mSuccessAmbig5_fixed_extended_Polar)
```


## D. Interaction fixed effects against main fixed effects

We compare the power for the fixed Imprecision interaction effect with that of the fixed main effect.


First, we check the simulated current power for the interaction fixed effects:

```{r ReceivingNews2 Model 2 current power, echo=FALSE}
ps_mSuccessAmbigInt_fixed
```


We simulate the power for 80, 150, 200 and 250 subjects, lower the fixed effect at -0.25 and compare the model to only specified fixed effects in the alternative model. The simulated power for the interaction is:

```{r ReceivingNews2 Model 2 Int vs Main predicted power - Plot, echo=FALSE}
plot(p_curve_interaction_success)
```

# To exceed the 95% Power for Imprecision main effect, with a fixed effect lower than that of the first wave, we need to exceed 200 participants. We will aim for 250 participants.