---
title: "ReceivingNews - Bayesian models"
editor_options: 
  markdown: 
    wrap: 72
---

```
By Valentin Guigon
June 2023
```


```{r, setup, include=FALSE}
rm(list = ls(all.names = TRUE)) #will clear all objects includes hidden objects.
gc() #free up memory and report the memory usage

list.of.packages <- c("rprojroot") 
{
  new.packages <- list.of.packages[!(list.of.packages %in% installed.packages()[,"Package"])]
  if(length(new.packages)) install.packages(new.packages)
  lapply(list.of.packages, require, character.only = TRUE)
}

project_root = find_rstudio_root_file()
knitr::opts_knit$set(root.dir = paste(project_root,"/outputs/reports", sep=""))

load(paste(project_root, "/R_environments/ReceivingNews-Bayesian_models_env.RData", sep=""))

```


### A. Bayesian models of success probability between waves

We compare the probabilities of success p1 and p2 for wave 1 and wave 2:

```{r probability of success between years, echo=FALSE}

print(out_success_year$BUGSoutput$summary)
```





### B. Bayesian models of success probability between groups

We compare the probabilities of success p1 and p2 for group 1 and group
2:

```{r probability of success between groups, echo=FALSE}

print(out_success_group$BUGSoutput$summary)
```





### C. Bayesian models of reception probability between waves

We compare the probabilities of reception p1 and p2 for wave 1 and wave
2:

```{r probability of reception between waves, echo=FALSE}

print(out_rec_year$BUGSoutput$summary)
```

Using the odds-ratio, the first wave has 1.19 times the odds of choosing
to receive additional news than the second wave:

```{r Odds-ratio for probability of reception between waves, echo=TRUE}
# Odds ratio
pA = out_rec_year$BUGSoutput$mean$p1
pB = out_rec_year$BUGSoutput$mean$p2
OR = (pA/(1-pA)) / (pB/(1-pB))
OR
```





### D. Bayesian models of reception probability between groups

We compare the probabilities of reception p1 and p2 for group 1 and
group 2:

```{r probability of reception between groups, echo=FALSE}

print(out_rec_group$BUGSoutput$summary)
```

Using the odds-ratio, the first group has 1.19 times the odds of
choosing to receive additional news than the second group:

```{r Odds-ratio for probability of reception between groups, echo=TRUE}
# Odds ratio 2nd group vs 1st group
pA = out_rec_group$BUGSoutput$mean$p2
pB = out_rec_group$BUGSoutput$mean$p1
OR = (pA/(1-pA)) / (pB/(1-pB))
OR
```





### E. Bayesian models of reception probability between veracity (not used in paper)

We compare the probabilities of reception p1 and p2 for false and true news
news:

```{r probability of reception between veracity, echo=FALSE}

print(out_rec_veracity$BUGSoutput$summary)
```





### F. Bayesian models of reception probability between judgments

We compare the probabilities of reception p1 and p2 for news judged as
false and news judged as true:

```{r probability of reception between judgments, echo=FALSE}

print(out_rec_veracity$BUGSoutput$summary)
```





### G. Bayesian models of WTP between waves

We compare the WTP mu1 and mu2 for wave 1 and wave 2

```{r differences in WTP between waves, echo=FALSE}


print(out_WTP_year$BUGSoutput$summary)
```





### H. Bayesian models of WTP between groups

We compare the WTP mu1 and mu2 for group 1 and group 2

```{r differences in WTP between groups, echo=FALSE}
print(out_WTP_group$BUGSoutput$summary)
```





### I. Bayesian models of WTP between reception choices

We compare the WTP mu1 and mu2 for choice not to receive and choice to
receive

```{r differences in WTP between reception choices, echo=FALSE}

print(out_WTP_rec$BUGSoutput$summary)
```





### J. Bayesian models of WTP between waves for reception choices

We compare the WTP for choices not to receive and choices to receive
between waves. 

Mu 1 is a choice not to receive in wave 1; mu 2 is a choice to receive in wave 1; 
mu 3 is a choice not to receive in wave 2; mu 4 is a choice to receive in wave 2:

```{r differences in WTP between waves for reception choices, echo=FALSE}

print(out_WTP_rec_years$BUGSoutput$summary)
```

