---
title: "ReceivingNews - Inter Rater Reliability"
editor_options: 
  markdown: 
    wrap: 72
---

```
By Valentin Guigon
June 2023
```


```{r, setup, include=FALSE}
rm(list = ls(all.names = TRUE)) #will clear all objects includes hidden objects.
gc() #free up memory and report the memory usage


list.of.packages <- c("R.matlab", "psych",
                      "rprojroot") 
{
  new.packages <- list.of.packages[!(list.of.packages %in% installed.packages()[,"Package"])]
  if(length(new.packages)) install.packages(new.packages)
  lapply(list.of.packages, require, character.only = TRUE)
}

project_root = find_rstudio_root_file()
knitr::opts_knit$set(root.dir = paste(project_root,"/outputs/reports", sep=""))

```

```{r ,load data and variables, include=FALSE}

load(paste(project_root, "/R_environments/ReceivingNews-Stimuli_ICC_env.RData", sep=""))
mean_ICC <- read.csv(paste("../../data/processed/ICC.csv", sep=""))
names(mean_ICC)[names(mean_ICC) == "ambiguity"] <- "imprecision"
mean_ICC$consensuality = 10 - mean_ICC$split # consensuality is the inverse of split

```

# Reliability on news dimensions

We use the package 'psych' to compute the IntraClass Correlations. We focus on the ICC2k.

ICC2: A random sample of k judges rate each target. The measure is one of absolute agreement in the ratings.  
Then, the reliability is estimated for the average of k ratings.  

### A. IntraClass Correlations for imprecision:

As shown below, a moderate degree of reliability was found between imprecision measurements. The average measure ICC was 0.54 with a 95% confidence interval from 0.4 to .66 (F(95,950)= 2.34, p<.001). 

```{r ICC imprecision, echo=FALSE}

ICC_imprecision
```

### B. IntraClass Correlations for consensuality

As shown below, a high degree of reliability was found between consensuality measurements. The average measure ICC was .81 with a 95% confidence interval from .75 to .87 (F(95,950)= 5.57, p<.001). 

```{r ICC consensuality, echo=FALSE}

ICC_consensuality
```

### C. IntraClass Correlations for desirability

As shown below, a moderate degree of reliability was found between desirability measurements. The average measure ICC was .59 with a 95% confidence interval from .46 to .7 (F(95,950)= 2.48, p<.001). 

```{r ICC desirability, echo=FALSE}

ICC_desirability
```